Predicting sales of newly published books

### 2015-10-19 paper.tex
working in the results section (updating tables and comments)

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analisys }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

%***************************************
\textbf{ TODO: add the table of results obtained using the variables selected taking into account the SOM analysis }

>>>>

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analysis }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with X variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}
